---
title: "Communications_Sector"
author: "Mandar"
date: "2022-08-26"
output: 
   html_document :
      code_folding: hide
      df_print: paged
      highlight: tango
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 2

---

```{r }
knitr::opts_chunk$set(echo = TRUE,fig.align = "center",
                        message = FALSE,
                      warning = FALSE)
options(tinytex.verbose = TRUE)
```

# loading the libraries

```{r}
library(tidymodels)
library(tidyquant)
library(tidyverse)
library(scales)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(plotly)
library(timetk)
library(modeltime)
library(DataExplorer)
library(correlationfunnel)
```
#The communication services sector is the newest of the GICS sectors and includes a couple of major areas that used to be part of other sectors. Telecommunication services providers, including both wireless telecom networks and providers of old-style landline services, make up one wing of the sector. At the other end are media and entertainment companies, including both older media like television and radio and interactive media via the internet and newer forms of communication.

# Data for Communications Sector
```{r}
# tickers
symbols <- c("VZ","T","DIS","CMCSA","USM") %>% sort()
# stock prices
# stock prices
prices  <- symbols %>%
    tq_get(get = "stock.prices", from = "1990-01-01")
# returns
returns <- prices %>%
    group_by(symbol) %>%
    tq_transmute(
        select = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly",
    ) %>%
    ungroup() %>%
    mutate(date = rollback(date, roll_to_first = TRUE))
returns

```
#Visualization of returns
```{r}
returns %>%
    group_by(symbol) %>%
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::percent) +
    theme_tq() + facet_wrap(~symbol) + 
    labs(
        title = "Monthly returns",
        subtitle = "Communications Sector",
        x = "",
        y = "Monthly Returns"
    ) + theme(legend.position = "none")
```
# Stock Prices Visualization

```{r}
prices %>%
    group_by(symbol) %>%
    plot_time_series(
        .date_var = date,
        .value = adjusted,
        .color_var = symbol,
        .facet_ncol = 2,
        .facet_scales = "free_y",
        .smooth = FALSE,
        .title = "Stock Prices Communications Sector",
        .x_lab = "",
        .y_lab = "Adjusted Prices",
        .legend_show = FALSE
    )
```


# Portfolio construction


```{r }
# Weights Allocation
w <- rep(1/5, 5)
# Portfolio creation
port_ret_tbl <- returns %>%
    tq_portfolio(
        assets_col = symbol, 
        returns_col = monthly.returns,
        weights = w
    ) %>%
    mutate(date = rollback(date, roll_to_first = TRUE)) %>%
    add_column(symbol ="Portfolio", .before = 1)

#Visualization
port_ret_tbl  %>%
    ggplot(aes(date, portfolio.returns)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous(labels = scales::percent) + theme_tq() + scale_color_tq() +
    labs(
        title = "Portfolio Returns",
        subtitle = "Communications Sector",
        y = "Returns",
        x = ""
    )

```
# timetk
```{r}
port_ret_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = portfolio.returns,
        .title = "Portfolio Returns Communications Sector",
        .x_lab = "",
        .y_lab = "Returns"
    )
```
# S&P500
```{r}
market_prices <- tq_get("^GSPC", get = "stock.prices",from = "1990-01-01")
market_returns <-  market_prices %>%
    tq_transmute(select = adjusted,
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "market_ret") %>%
    mutate(date = rollback(date, roll_to_first = TRUE))
market_returns
```
# FAMA-FRENCH FACTORS
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date,"01")),"month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) %>%
  # filter the dates 
  filter(date >= "1990-01-01")

factors_ff_monthly 
```
# Combining all the data
```{r}
port_risk_market_tbl <- port_ret_tbl %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = portfolio.returns - rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    select(symbol, date, mkt_excess, smb, hml, excess_returns, market_excess_returns)
```
# Beta Estimation 
## step1:CAPM function
```{r}
library(slider)
# estimate capm
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
  } else {
    fit <- lm(excess_returns ~ mkt_excess + smb+hml+ market_excess_returns, data = data)
    beta <- as.numeric(fit$coefficients[2])
  }
  return(beta)
}
# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- bind_rows(data) |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )

  tibble(
    month = unique(data$date),
    beta = betas
  )
}
```

## step2: Beta estimation
```{r}
beta_port_tbl <- port_risk_market_tbl %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    drop_na() %>%
    select(symbol, date, beta)
```
## step3: Beta Visualization 
```{r}
beta_port_tbl %>%
    ggplot(aes(date, beta)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous() + theme_tq() + scale_color_tq() +
    labs(
        title = "Rolling Beta using 5 years data",
        subtitle = "Communications Sector",
        caption = "Stocks(VZ, DIS, CMCSA, T, USM)",
        x ="",
        y="Beta"
    )
```
#timetk
```{r}
beta_port_tbl %>%
    plot_time_series(
        .value = beta,
        .date_var = date,
        .title = "Rolling Beta Communications Sector"
        
    )
```
# # Stock Returns , Fama-French and S&P 500
```{r}
# combining the data
returns_risk_market_tbl <- returns %>%
    group_by(symbol) %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = monthly.returns -rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, excess_returns, market_excess_returns, mkt_excess, smb, hml)
```
## Beta Estimation for Stocks
```{r}
beta_stocks_tbl <- returns_risk_market_tbl %>%
    group_by(symbol) %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, beta)
beta_stocks_tbl

```
# Beta Visualization
```{r}
beta_stocks_tbl %>%
    ggplot(aes(date, beta, color = symbol)) +
    geom_line() + scale_y_continuous() +
    theme_tq() +
    labs(
        title = "Rolling beta with 5 years of data",
        subtitle = "communications Sector ",
        capition = "stocks(CMCSA, USM,DIS, T, VZ)",
        y ="Beta",
        x =""
    ) 
```
#timetk
```{r}
beta_stocks_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = beta,
        .color_var = symbol,
        .smooth = FALSE,
        .title = "Rolling Beta for Stocks (Communications Sector)",
        .x_lab = "",
        .y_lab = "Beta"
    )
```
 






