---
title: "Consumer_Staples_Sector"
author: "Mandar"
date: "2022-10-02"
output: 
    html_document:
        theme : united
        code_folding : hide
        df_print: paged
        highlight: tango
        number_sections: TRUE
        toc: yes
        toc_depth: 2
        smooth_scroll: TRUE
        
---

```{r }
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE,
    out.width = "200%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```
# Libraries

```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)
library(broom)
library(tidymodels)
library(slider)
library(scales)
library(timetk)


```

# Consumer Staples :
The Procter & Gamble Company"PG",
The Coca-Cola Company"KO",
Costco "COST",
Walmart "WMT",
The Kroger Co."KR"

```{r}
symbols <- c("PG","KO","COST","WMT","KR") |> sort()
prices <- symbols |> 
    tq_get(get = "stock.prices", from = "1990-01-01")

prices |> 
    group_by(symbol) |> 
    summarise(
        min_date = min(date),
        max_date = max(date)
    )

```
```{r}
 prices |> 
    group_by(symbol) |>
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::dollar) + theme_tq() +
    scale_color_tq(theme = "dark") +
    labs(
        title = "Adjusted Stock prices ",
        subtitle = "Downward Trend",
        caption = "selected Consumer-Staple stocks",
        y = "Adjusted Prices",
        x = ""
    )
```
```{r}
prices |> 
    plot_time_series(
        .date_var = date,
        .value = adjusted,
        .color_var = symbol,
        .facet_scales = "free_y",
        .title = "Adjusted Prices for Selected Consumer-Staple Stocks ",
        .x_lab = "",
        .y_intercept = 0,
        .y_intercept_color = "Black",
        .y_lab = "Adjusted Prices($)",
        .smooth = FALSE
    )
```

# Stock Returns
```{r}
returns_tbl <- prices |> 
    group_by(symbol) |> 
    tq_transmute(
        select     = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly"
        
    ) |> 
    ungroup() |> 
    mutate(date = rollback(date, roll_to_first = TRUE))

returns_tbl

```
# Visualization of Stock Returns
```{r}
returns_tbl |> 
    group_by(symbol) |> 
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + facet_wrap(~symbol)+
    scale_y_continuous(labels = scales::percent) + scale_color_tq(theme = "dark") +
    theme(legend.position = "none")+
    labs(
        title = "Monthly Returns for Selected Consumer-Staple Stocks",
        subtitle = "Periods of Volatility are : 2000,2008,2020",
        x = "",
        y = "Returns"
    )
```
```{r}
returns_tbl |> 
    plot_time_series(
        .date_var = date,
        .color_var = symbol,
        .value = monthly.returns * 100,
        .facet_ncol = 2,
        .facet_vars = symbol,
        .facet_scales = "free_y",
        .title = "Monthly Returns for selected Consumer-Staple Stocks",
        .y_intercept = 0,
        .y_lab = "Returns(%) ",
        
        .x_lab = "",
        .y_intercept_color = "Black",
        .smooth = FALSE,
        .legend_show = FALSE
    )
```
# Portfolio 

```{r}
# assets
n <- length(symbols)
#weight
w <- rep(1,n)/n

port_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    tq_portfolio(
        assets_col   = symbol,
        returns_col  = monthly.returns,
        weights      = w,
        rebalance_on = "years"
        
    )
port_tbl
```
# Visualiaztion of Portfolio Returns
```{r}
port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = portfolio.returns * 100,
        .smooth = FALSE,
        .title = "Portfolio Returns for Consumer-Staples Sector",
        .x_lab = "",
        .y_lab = "Returns",
        .y_intercept = 0,
        .y_intercept_color = "BLUE"
    )
```
# Fama-French Factors
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |> 
  transmute(
    date = floor_date(ymd(str_c(date, "01")), "month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) |>
  filter(date >= "1990-01-01")

factors_ff_monthly
```
# Combining Returns and Fama-French
```{r}
returns_risk_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = monthly.returns - rf) |> 
    ungroup() |> 
    select(symbol, date, excess_returns:mkt_excess)
returns_risk_tbl
```
# Beta Estimation for Stock Returns
## Function for estimation
```{r}
library(slider)
#  capm estimation
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
   
  } else {
    fit <- lm(excess_returns ~ mkt_excess + hml + smb , data = data)
    # note that we take into account the coefficient of mkt_excess
    beta <- as.numeric(coefficients(fit)[2])
    
  }
  return(beta)
}

# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- data |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~ estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )
  
  return(tibble(
    month = unique(data$date),
    beta = betas
   
  ))
}
```
## Beta Estimation for Returns
```{r}
beta_estimation_tbl <- returns_risk_tbl |> 
    group_by(symbol) |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(symbol, date, beta) |> 
    drop_na() |> 
    ungroup()
beta_estimation_tbl
```
# Visualization of Beta for individual stock 
```{r}
beta_estimation_tbl  |> 
    plot_time_series(
        .date_var          = date,
        .value             = beta,
        .color_var         = symbol,
        .title             = "Beta Estimates for Selected Consumer-Staple Stocks" ,
        .y_intercept       = 0,
        .y_intercept_color = "Black",
        .x_lab             = "",
        .y_lab             = "Beta",
        .smooth            = FALSE,
        .legend_show       = FALSE
    )
```
# Combining Portfolio and Fama-French

```{r}
port_risk_tbl <- port_tbl |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = portfolio.returns -rf) |> 
    select(date, excess_returns:mkt_excess)

port_risk_tbl
```
# Beta Estimation for Portfolio Returns
```{r}
beta_port_tbl <- port_risk_tbl |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(date, beta) |> 
    drop_na()
beta_port_tbl

```
# Visualization of Beta Estimates for Portfolio

```{r}
beta_port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = beta,
        .y_intercept = 0,
        .y_intercept_color = "Black",
        .y_lab = "Beta",
        .x_lab = "",
        .title = "Beta Estimates of Portfolio for Consumer-Staple Sector ",
        .smooth = FALSE
    )
```
# Visualization with ggplot
```{r}
b <- beta_port_tbl |> 
    ggplot(aes(date, beta))+
    geom_line() + theme_tq() +
    scale_color_tq(theme = "dark") +
    labs(
        title = "Beta Estimates of Portfolio for Consumer-Staple Sector",
        subtitle = "Estimates suggest that Portfolio is less volatile than the markets",
        x = "",
        y = "Beta"
    )

ggplotly(b)
```











