---
title: "Consumer_Discretionary"
author: "Mandar"
date: "2022-10-02"
output:
    html_document :
        code_folding: show
        df_print: paged
        highlight: tango
        number_sections: yes
        theme: flatly
        toc: true
        toc_depth: 2
---
```{r}
knitr::opts_chunk$set(echo = TRUE,fig.align = "center",
                        message = FALSE,
                      warning = FALSE)
options(tinytex.verbose = TRUE)
```

# Libraries 
```{r}
library(tidymodels)
library(tidyquant)
library(tidyverse)
library(scales)
library(lubridate)
library(ggplot2)
library(plotly)
library(timetk)
library(modeltime)
library(slider)

```

#Consumer Discretionary Sector: 
##Target "TGT",
##Nike "NKE",
##Mcdonald Corporation "MCD",
##The Home Depot, Inc."HD",
##Carnival Corporation & plc "CCL"

```{r}
symbols <- c("TGT","NKE","MCD","HD","CCL") |> sort()

prices <- symbols |> 
    tq_get(get = "stock.prices", from = "1990-01-01")
prices

```
# Visualization of Stock Prices
```{r}
prices |> 
    group_by(symbol) |> 
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::dollar) +
    theme_tq() + scale_color_tq(theme = "dark") +
    labs(
        title = " Selected Consumer-Discretionary Stock Prices",
        subtitle = "Downward Trend observed for the recent period",
        x = "",
        y = "Adjusted Price"
    )
```
# Interactive Plot
```{r}
prices |> 
    plot_time_series(
        .date_var          = date,
        .value             = adjusted,
        .color_var         = symbol,
        .facet_scales      = "free_y",
        .y_intercept       = 0,
        .y_intercept_color = "Black",
        .title             = "Selected Consumer-Discretionary Stock Prices",
        .smooth            = FALSE,
        .y_lab = "Adjusted Prices($)",
        .legend_show = FALSE
    )
```

# Monthly Returns

```{r}
returns_tbl <- prices |> 
    group_by(symbol) |> 
    tq_transmute(
        select = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly"
    ) |> 
    ungroup() |> 
    mutate(date = rollback(date, roll_to_first = TRUE))

returns_tbl
```
# Visualization of Monthly Returns 
```{r}
returns_tbl |> 
    group_by(symbol) |> 
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line()  + facet_wrap(~ symbol) + scale_y_continuous(labels = scales::percent) +
    theme_tq() + scale_color_tq(theme = "dark") +
    labs(
        title = "Monthly Returns of Selected Consumer-Discretionary Stocks",
        subtitle = "Periods of Volatility observed at 2000,2008,2021",
        x = "",
        y = "Returns"
    ) +
    theme(legend.position = "none")
```
# Interactive Plot
```{r}
returns_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = monthly.returns,
        .smooth = FALSE,
        .color_var = symbol,
        .facet_vars = symbol,
        .facet_scales = "free_y",
        .facet_ncol = 2,
        .y_intercept = 0,
        .y_intercept_color = "BLACK",
        .title = "Monthly Returns of Selected Consumer-Discretionary Stocks",
        .x_lab = "",
        .y_lab = "Returns",
        .legend_show = FALSE
    )
```

# FAMA-FRENCH 3 factors
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date,"01")),"month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) %>%
  # filter the dates 
  filter(date >= "1990-01-01")

factors_ff_monthly 

```
# Combining the Stock Returns and Fama-French

```{r}
returns_risk_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = monthly.returns - rf) |> 
    select(symbol, date, excess_returns:mkt_excess)

returns_risk_tbl

```
# CAPM Estimation
```{r}

estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
   
  } else {
    fit <- lm(excess_returns ~ mkt_excess + hml + smb , data = data)
    # note that we take into account the coefficient of mkt_excess
    beta <- as.numeric(coefficients(fit)[2])
    
  }
  return(beta)
}

# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- data |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~ estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )
  
  return(tibble(
    month = unique(data$date),
    beta = betas
   
  ))
}
```
# Beta Estimation
```{r}
beta_estimation_tbl <- returns_risk_tbl |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(symbol, date, beta) |> 
    drop_na() |> 
    ungroup()


beta_estimation_tbl
    
```
# Visualization of Beta for stock returns
```{r}
beta_estimation_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = beta,
        .smooth = FALSE,
        .color_var = symbol,
        .facet_scales = "free_y",
        .y_intercept = 0,
        .y_lab = "Beta",
        .x_lab = "",
        .y_intercept_color = "BLACK",
        .title = "Beta Estimates for Selected Consumer Discretionary Stocks",
        .legend_show = FALSE
    )
```
# Portfolio Construction:
```{r}
n <- length(symbols)
#weights
w <- rep(1,n)/n

port_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    tq_portfolio(
        assets_col   = symbol,
        returns_col  = monthly.returns,
        weights      = w,
        rebalance_on = "years"
    )
port_tbl
```
# Visualization of Portfolio Returns

```{r}
port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = portfolio.returns,
        .title = "Portfolio Returns of Consumer Discretionary Sector",
        .y_intercept = 0,
        .y_intercept_color = "BLUE",
        .y_lab = "Returns",
        .x_lab = "",
        .smooth = FALSE
    )
```
# Combining the Portfolio Returns and the Fama-French Factors

```{r}
port_risk_tbl <- port_tbl |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = portfolio.returns - rf) |> 
    select(date,excess_returns:mkt_excess)
port_risk_tbl
```
# Beta Estimation :
```{r}
beta_port_tbl <- port_risk_tbl |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(date, beta) |> 
    drop_na()

beta_port_tbl
```
# Visualization of Beta
```{r}

beta_port_tbl |> 
    ggplot(aes(date, beta)) +
    geom_line() + theme_tq() + scale_color_tq(theme = "dark") +
    labs(
        title = "Beta Estimates of  Portfolio  ",
        subtitle = " Consumer-Discretionary Sector",
        x = "",
        y = ""
    )
```
# Interactive Plot
```{r}
beta_port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = beta,
        .smooth = FALSE,
        .y_intercept = 0,
        .y_intercept_color = "BLUE",
        .title = "Beta Estimates of Portfolio for Consumer-Discretionary Sector ",
        .x_lab = "",
        .y_lab = "Beta"
    )

```
# Recent times point towards increase in volatility of our portfolio compared to market.








