---
title: "Health-Care"
author: "Mandar"
date: "2022-09-30"
output: 
    html_document:
        theme : united
        code_folding : hide
        df_print: paged
        highlight: tango
        number_sections: TRUE
        toc: yes
        toc_depth: 2
        smooth_scroll: TRUE
        
---

```{r setup}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE,
    out.width = "200%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```

# loading the libraries

```{r}
library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)
library(broom)
library(tidymodels)
library(slider)
library(scales)
library(timetk)

```

# Health-Care : We select a blend of Pharmaceutical and Health-Care companies
Pfizer(PFE) 
Johnson&Johnson(JNJ)
Bristol-Myers Squibb (BMY)
CVS Health Corporation (CVS)
Abbott Laboratories   (ABT)

```{r}
# tickers
symbols <- c("PFE","ABT","BMY","CVS","JNJ") |> sort()

prices <- symbols |> 
    tq_get(get = "stock.prices", from = "1990-01-01")

prices 
```
# Visualization of Prices
```{r}
prices |> 
    group_by(symbol) |>
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::dollar) + theme_tq() +
    scale_color_tq(theme = "dark") + 
    labs(
        title = " Health-Care Stocks Adjusted Prices",
        subtitle = "rising Trend",
        x = "",
        y = "Adjusted"
    )
``` 
# interactive plot for the stock prices
```{r}
library(timetk)
prices |> 
    plot_time_series(
        .date_var = date,
        .value    = adjusted,
        .color_var = symbol,
        .smooth = FALSE,
        .y_lab = "adjusted prices($)",
        .x_lab = "",
        .title = "Adjusted Stock Prices of Health-Care Companies",
        .legend_show = FALSE
        
    )
```
# Monthly Returns :
```{r}
returns_tbl <- prices |> 
    group_by(symbol) |> 
    select(symbol, date, adjusted) |> 
    tq_transmute(
        select = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly"
    ) |> 
    ungroup() |> 
    mutate(date = rollback(date, roll_to_first = TRUE))
returns_tbl
```

# Visualization of returns- 
## Interactive Plot

```{r}
returns_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = monthly.returns,
        .color_var = symbol,
        .y_lab = "Returns(%)" ,
        .facet_vars = symbol,
        .facet_ncol = 2,
        .facet_scales = "free_y",
        .smooth = FALSE,
        .title = "Monthly Returns for Health-Care Stocks",
        .y_intercept = 0,
        .y_intercept_color = palette_green()[[1]],
        .legend_show = FALSE
    )

```

## GGPLOT Visualization

```{r}
returns_tbl |> 
    group_by(symbol) |> 
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + facet_wrap(~symbol) +
    scale_y_continuous(labels = scales::percent) +
    theme_tq() + scale_color_tq(theme = "dark")  + theme(legend.position = "none") +
    labs(
        title = "Monthly Returns",
        subtitle = "High Volatility periods 2000, 2008",
        x ="",
        y = "Returns"
    )
    
```


# Portfolio Construction: Equal Weight Allocation

```{r}
# number of assets
n <- length(symbols)

# weight allocation
w <- rep(1,n)/n

port_tbl <- returns_tbl |> 
    tq_portfolio(
        assets_col     = symbol,
        returns_col    = monthly.returns,
        weights        = w,
        rebalance_on   = "years"
    )
port_tbl
```


# portfolio visualization

```{r}
port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = portfolio.returns,
        .title = "Portfolio Returns Health-Care Sector"
    )

```
# Fama-French Factors: 3 Factors considerd with Monthly Frequency
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date, "01")), "month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) |>
  filter(date >= "1990-01-01")

factors_ff_monthly

```
# Returns and Fama-French Factors
```{r}
returns_risk_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = monthly.returns - rf) |> 
    select(symbol, date, excess_returns:mkt_excess) |> 
    ungroup()

```
# CAPM Function :

```{r}
library(slider)
#  capm estimation
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
   
  } else {
    fit <- lm(excess_returns ~ mkt_excess + hml + smb , data = data)
    # note that we take into account the coefficient of mkt_excess
    beta <- as.numeric(coefficients(fit)[2])
    
  }
  return(beta)
}

# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- data |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~ estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )
  
  return(tibble(
    month = unique(data$date),
    beta = betas
   
  ))
}

```
## Beta Estimation for Asset Returns
```{r}
beta_estimate_tbl <- returns_risk_tbl |> 
    group_by(symbol) |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(symbol, date, beta) |> 
    drop_na() |> 
    ungroup()

beta_estimate_tbl 
    
```
# Visualization of Beta
```{r}
beta_estimate_tbl |>
    group_by(symbol) |> 
    ggplot(aes(date, beta, color = symbol)) +
    geom_line() +
    theme_tq() + scale_color_tq(theme = "dark") +
    labs(
        title = "Monthly Beta Estimates",
        subtitle = "Exposure is less than 1",
        caption = "Selected Health-Care Stocks",
        x = "",
        y = "Beta"
    )
```
#Interactive plot 
```{r}
beta_estimate_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = beta,
        .color_var = symbol,
        .smooth = FALSE,
        .title = "Monthly Beta Estimates for selected Health-Care Stocks",
        .x_lab = "",
        .y_intercept = 0,
        .legend_show = FALSE
    )
```

# Thus the exposure is less than 1 for most of the health care stocks from 2021-2022*          [* :- current]
```{r}
port_risk_tbl <- port_tbl |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = portfolio.returns -rf) |> 
    select(date, excess_returns:mkt_excess)

port_risk_tbl
```
```{r}
beta_port_tbl <- port_risk_tbl |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(date, beta) |> 
    drop_na()

beta_port_tbl
```
# Beta Visualization for Portfolio
```{r}
beta_port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = beta,
        .smooth = FALSE,
        .y_intercept = 0,
        .y_intercept_color = "RED",
        .title = "Monthly Beta Estimates Health-Sector Portfolio",
        .x_lab = "",
        .y_lab = "Beta"
    )
```

# What is observed is that Beta is less than 1, so less volatile compared to market returns


