---
title: "Industrials_Sector"
author: "Mandar"
date: "2022-08-25"
output: 
   html_document :
      code_folding: hide
      df_print: paged
      highlight: tango
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 2
---

```{r }
knitr::opts_chunk$set(echo = TRUE,fig.align = "center",
                        message = FALSE,
                      warning = FALSE)
options(tinytex.verbose = TRUE)

```
# loading the libraries


```{r }
library(tidymodels)
library(tidyquant)
library(tidyverse)
library(scales)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(plotly)
library(timetk)
library(modeltime)
library(DataExplorer)
library(correlationfunnel)

```

# The industrial goods sector includes companies involved with aerospace and defense, industrial machinery, tools, lumber production, construction, waste management, manufactured housing, and cement and metal fabrication. Performance in the industrial goods sector is largely driven by supply and demand for building construction in the residential, commercial, and industrial real estate segments, as well as the demand for manufactured products.When the economy contracts during recessions, activity in this sector drops because companies postpone expansion and produce fewer goods. However, with this sector covering a wide range of subsectors, there is usually at least one area of growth in the industrial goods sector. The industrial goods sector goes through life cycles that see different subsectors in growth phases.

# Data for Industrial Sector
```{r}
symbols <- c("GE","HON","BA","CAT","CMI") %>% sort()

prices <- symbols %>% 
    tq_get(
        get = "stock.prices", from ="1990-01-01"
    )
returns <- prices %>%
    group_by(symbol) %>%
    tq_transmute(
        select = adjusted,
        mutate_fun = periodReturn,
        period    = "monthly",
       ) %>%
    ungroup() %>%
    mutate(date = rollback(date, roll_to_first = TRUE))

# Visualization of Returns
returns %>%
    group_by(symbol) %>%
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::percent) +
    theme_tq() + facet_wrap(~ symbol) +
    labs(
        title = "Returns of stocks",
        subtitle = "Industrial Sector",
        caption = "Stocks(CAT,BA,HON,GE,CMI)",
        x ="",
        y="Monthly Returns"
    ) + theme(legend.position = "none")

```
# Portfolio Construction
```{r}
w <- rep(1/5, 5)

port_ret_tbl <- returns %>%
    tq_portfolio(
        assets_col = symbol, 
        returns_col = monthly.returns,
        weights = w
    ) %>%
    mutate(date = rollback(date, roll_to_first = TRUE)) %>%
    add_column(symbol ="Portfolio", .before = 1)
port_ret_tbl  %>%
    ggplot(aes(date, portfolio.returns)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous(labels = scales::percent) + theme_tq() + scale_color_tq() +
    labs(
        title = "Portfolio Returns ",
        subtitle = "Industrial Sector",
        caption = "Stocks(BA,CAT,HON,GE,CMI)",
        x ="",
        y = "Monthly Returns"
    )
```
# Portfolio Returns Visualization
```{r}
port_ret_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = portfolio.returns,
        .title = "Portfolio Returns",
        .x_lab = "",
        .y_lab = "Monthly Returns"
    )
```
# S&P 500 data
```{r}
market_prices <- tq_get("^GSPC", get = "stock.prices",from = "1990-01-01")
market_returns <-  market_prices %>%
    tq_transmute(select = adjusted,
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "market_ret") %>%
    mutate(date = rollback(date, roll_to_first = TRUE))

```
# Fama-French Data
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date,"01")),"month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) %>%
  # filter the dates 
  filter(date >= "1990-01-01")

factors_ff_monthly 
```
# Combining all the data
```{r}
port_risk_market_tbl <- port_ret_tbl %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = portfolio.returns - rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    select(symbol, date, mkt_excess, smb, hml, excess_returns, market_excess_returns)
```
# Beta Estimation 
## step1:CAPM function
```{r}
library(slider)
# estimate capm
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
  } else {
    fit <- lm(excess_returns ~ mkt_excess + smb+hml+ market_excess_returns, data = data)
    beta <- as.numeric(fit$coefficients[2])
  }
  return(beta)
}
# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- bind_rows(data) |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )

  tibble(
    month = unique(data$date),
    beta = betas
  )
}
```
## step2: Beta estimation
```{r}
beta_port_tbl <- port_risk_market_tbl %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    drop_na() %>%
    select(symbol, date, beta)
```
## step3: Beta Visualization
```{r}
beta_port_tbl %>%
    ggplot(aes(date, beta)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous() + theme_tq() + scale_color_tq() +
    labs(
        title = "Rolling Beta using 5 years data",
        subtitle = "Industrial Sector",
        caption = "Stocks(CAT, GE, BA, HON, CMI)",
        x ="",
        y="Beta"
    )
    
```
# Stock Returns , Fama-French and S&P 500
```{r}

returns_risk_market_tbl <- returns %>%
    group_by(symbol) %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = monthly.returns -rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, excess_returns, market_excess_returns, mkt_excess, smb, hml)
```

# Beta Estimation
```{r}
beta_stocks_tbl <- returns_risk_market_tbl %>%
    group_by(symbol) %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, beta)
``` 
# Beta Visualization
```{r}

beta_stocks_tbl %>%
    ggplot(aes(date, beta, color = symbol)) +
    geom_line() + scale_y_continuous() +
    theme_tq() +
    labs(
        title = "Rolling beta with 5 years of data",
        subtitle = "Industrial Sector",
        capition = "stocks(CAT, GE,HON, BA, CMI)",
        y ="Beta",
        x =""
    )
```
```{r}
beta_stocks_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = beta,
        .color_var = symbol,
        .smooth = FALSE,
        .title = "Rolling Beta With 5 years of Data",
        .x_lab = "",
        .y_lab = "Beta"
    )
```












