---
title: "Industrial_Sector"
author: "Mandar"
date: "2022-10-02"
output:
    html_document :
        code_folding: show
        df_print: paged
        highlight: tango
        number_sections: yes
        theme: flatly
        toc: true
        toc_depth: 2
        
---

```{r }
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE,
    out.width = "200%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```
# Industrial Sector:
General Electric Company (GE)
Honeywell International Inc. (HON)
The Boeing Company (BA)
Caterpillar Inc. (CAT)
Cummins Inc. (CMI)


```{r}
# tickers
symbols <- c("GE","HON","BA","CAT","CMI") |>  sort()

```
# loading the required libraries



```{r}
library(tidymodels)
library(tidyquant)
library(tidyverse)
library(scales)
library(lubridate)
library(ggplot2)
library(plotly)
library(timetk)
library(modeltime)

```
# Downloading the data


```{r}
# stock prices
prices <- symbols |> 
    tq_get(get = "stock.prices", from = "1990-01-01")
prices
```
# Visualization of Stock Prices
```{r}
prices |> 
    group_by(symbol) |> 
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::dollar) +
    theme_tq() + scale_color_tq(theme = "light") +
    labs(
        title    = "Adjusted Stock Prices",
        subtitle = "Downward Trend is observed",
        caption  = "Selected Industrial Stocks",
        x = "",
        y = "Adjusted Price"
    )
```
# Stock Returns
```{r}
returns_tbl <- prices |> 
    group_by(symbol) |> 
    select(symbol, date, adjusted) |> 
    tq_transmute(
        select     = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly",
    ) |> 
    ungroup() |> 
    mutate(date = rollback(date, roll_to_first = TRUE))

returns_tbl 
```
# Visualization of Stock Returns with monthly frequency

```{r}
returns_tbl |> 
    group_by(symbol) |> 
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + facet_wrap(~symbol) + theme_tq() +
    scale_y_continuous(labels = scales::percent) +
    scale_color_tq(theme = "dark")  + theme(legend.position = "none") +
    labs(
        title = "Monthly Returns of selected Industrial Stocks",
        subtitle = "Periods of volatility: 2000,2008,2020",
        x = "",
        y = "Returns"
    )
    

```
# Interactive Plot for Stock Returns
```{r}
returns_tbl |> 
    plot_time_series(
        .date_var    = date,
        .value       = monthly.returns,
        .color_var   = symbol,
        .facet_vars  = symbol,
        .facet_ncol  = 2,
        .smooth      = FALSE,
        .y_intercept = 0,
        .y_intercept_color = "BLACK",
        .y_lab       = "Returns",
        .x_lab       = "",
        .title       = "Monthly Returns of Selected Indusrial Stocks",
        .legend_show = FALSE,
        .facet_scales = "free_y"
    )

```
# FAMA-FRENCH 3 FACTORS
```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date,"01")),"month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) %>%
  # filter the dates 
  filter(date >= "1990-01-01")

factors_ff_monthly 
```
# Combining the Stock Returns and FAMA-FRENCH Data

```{r}
returns_risk_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = monthly.returns -rf) |> 
    ungroup() |> 
    select(symbol, date, excess_returns:mkt_excess)


returns_risk_tbl

```
# Beta Estimation 
## STEP 1: CAPM Function


```{r}
library(slider)
#  capm estimation
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
   
  } else {
    fit <- lm(excess_returns ~ mkt_excess + hml + smb , data = data)
    # note that we take into account the coefficient of mkt_excess
    beta <- as.numeric(coefficients(fit)[2])
    
  }
  return(beta)
}

# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- data |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~ estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )
  
  return(tibble(
    month = unique(data$date),
    beta = betas
   
  ))
}

```

## STEP 2: Beta

```{r}
beta_estimation_tbl <- returns_risk_tbl |> 
    group_by(symbol) |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(symbol, date, beta) |> 
    drop_na() |> 
    ungroup()

beta_estimation_tbl

```
# Visualization of Beta for Stock Returns
```{r}
beta_estimation_tbl |> 
    group_by(symbol) |> 
    ggplot(aes(date, beta, color = symbol)) +
    geom_line() + theme_tq() + scale_color_tq(theme = "light") +
    labs(
        title = "Monthly Beta Estimates for selected Industrial Stocks",
        subtitle = "The stock returns are volatile than the overall market",
        x        = "",
        y        = "Beta"
    )

```
# Interactive Plot for Beta
```{r}
beta_estimation_tbl |> 
    plot_time_series(
        .date_var = date,
        .value    = beta,
        .color_var = symbol,
        .facet_scales = "free_y",
        .smooth = FALSE,
        .y_intercept = 0,
        .y_intercept_color = "ORANGE",
        .x_lab = "",
        .y_lab = "Beta",
        .title = "Monthly Beta Estimates for selected Industrial Stocks",
        .legend_show = FALSE
    )

```
# Portfolio Construction: Equal Weight Allocation
```{r}
# Assets
n <- length(symbols)
# weights
w <- rep(1,n)/n

port_tbl <- returns_tbl |> 
    group_by(symbol) |> 
    tq_portfolio(
        assets_col  = symbol,
        returns_col = monthly.returns,
        weights     = w,
        rebalance_on = "years"
    )
port_tbl
```
# Visualization of Portfolio Returns 
```{r}
port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = portfolio.returns,
        .smooth = FALSE,
        .title = "Portfolio Returns for Industrial Sector",
        .x_lab = "",
        .y_lab = "Returns",
        .y_intercept = 0,
        .y_intercept_color = "RED"
    )
```
# Combining the Portfolio Returns and FAMA-FRENCH 
```{r}
port_risk_tbl <- port_tbl |> 
    left_join(factors_ff_monthly, by = "date") |> 
    mutate(excess_returns = portfolio.returns -rf) |> 
    select(date, excess_returns:mkt_excess)
port_risk_tbl

```
# Beta Estimation for the Portfolio
```{r}
beta_port_tbl <- port_risk_tbl |> 
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) |> 
    select(date, beta) |> 
    drop_na()
```

# Visualization of Beta for Portfolio

```{r}
beta_port_tbl |> 
    ggplot(aes(date, beta)) +
    geom_line() + theme_tq() +
    scale_color_tq(theme = "Dark") +
    labs(
        title    = "Monthly Beta Estimate for Industrial-Sector Portfolio",
        subtitle = "Portfolio is more volatile compared to overall market",
        x        = "",
        y        = "Beta"
    )

```
# Interactive Visualization for Beta Estimates of Portfolio
```{r}
beta_port_tbl |> 
    plot_time_series(
        .date_var = date,
        .value = beta,
        .title = "Monthly Beta Estimates for Industrial-Sector Portfolio",
        .y_intercept = 0,
        .y_intercept_color = "RED",
        .x_lab = "",
        .y_lab = "Beta"
    )

```

# Conclusion: The Portfolio is more volatile in compared to overall market .














