---
title: "Michael_Bury_Portfolio"
author: "Mandar"
date: '2022-06-04'
output: 
  html_document:
      code_folding: show #or show
      df_print: paged #or tibble
      highlight: tango 
      number_sections: yes #or no
      theme: flatly #from bootswitch themes
      toc: yes #shows table of contents
      toc_depth: 2
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE, fig.height = 8)
```

# libraries

```{r }
library(tidyquant)
library(tidyverse)
library(lubridate)
library(purrr)
library(tidymodels)
library(timetk)
library(highcharter)
library(ggplot2)
library(tidyr)
library(webshot)
library(dplyr)
library(tidyr)
library(dplyr)
library(plotly)
```

# Downloading the 

```{r}
symbols <- c("AAPL","BMY","BKNG","WBD","GOOG","FB","CI","OVV","NXST","STLA","GPN","SPWH")

data <- symbols %>%
  tq_get(get = "stock.prices",from = "2000-01-01")

```
```{r}
data %>%
  group_by(symbol) %>%
  summarise(
    min_date = min(date),
    max_date = max(date)
  )
```
# So we need a common date, which is 2014-05-01
```{r}
data_reg_tbl <- data %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  filter(date>="2014-05-01") %>%
  ungroup() 

  
  
```
```{r}
returns_monthly <- data_reg_tbl %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  tq_transmute(
    select   = adjusted,
  mutate_fun = periodReturn,
  period     = "monthly"
  ) %>%
  ungroup() %>%
  mutate(date = rollback(date, roll_to_first = T))
  
  

```
```{r}
# Visualizations 
returns_monthly  %>% 
  ggplot(aes(monthly.returns)) +
  geom_density(aes(color = symbol), alpha = 0.3) +
  geom_histogram(aes(fill = symbol), alpha = 0.3, binwidth = 0.0009) +
  labs(
        title = "Monthly Spread of Stock Returns"
    ) +
    theme_tq() + theme(legend.position = "none") +
    facet_wrap(~ symbol, ncol = 4, nrow = 8) +
    ylab("") +
    xlab("Monthly Returns") +
    scale_x_continuous(labels = scales::percent)
  
```
```{r}
returns_monthly  %>%
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() +
    facet_wrap(~ symbol, scales = "free_y", ncol = 4, nrow =8) +
    theme_tq() +
    scale_y_continuous(labels = scales::percent) + theme(legend.position = "none") +
    geom_smooth(method = "lm") +
    labs(
        title = "Monthly Returns of the Funds (2014-2022)",
        
        caption  = "Michael Burry Portfolio",
        y = "Monthly Returns", x = ""
    )
```
```{r}
data_reg_tbl %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() +
    facet_wrap(~ symbol, scales = "free_y") +
    scale_y_continuous(labels = scales::dollar) +
    theme_tq() + scale_color_tq() +
    theme(legend.position = "none") +
    labs(
        title = "Adjusted Prices of the Stocks (2014-2022) ",
        
        caption = " Michael Burry Portfolio",
        y = "Adjusted Price", x = ""
    )
```
```{r}
returns_monthly  %>%
    group_by(symbol) %>%
    tq_performance(
        Ra = monthly.returns,
        performance_fun = SharpeRatio.annualized,
        scale = 12,
        Rf = 0.03/12
    ) %>%
    ungroup() %>%
    mutate(symbol = as.factor(symbol)) %>%
    mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`,2)) %>%
    ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() + 
    scale_color_tq() + 
    geom_label() +
    labs(title = "Annualized Sharpe Ratio (RFR = 3%)",

         caption = "Michael Burry Portfolio",
         y = "Sharpe Ratio",
         x = "Ticker Symbol")


```
# Creating the Portfolio based on Michael Buryy Philosophy
## Allocation of weights
#AAPL- 17.86% #BMY-10.88 #BKNG-9.33  #WBD - 9.3 #goog-8.98#CI-8.92,FB - 8.83#OVV-8.06#NXST-7.13#STLA-4.85#GPN-4.53#SPWH-1.33


```{r}
w <- c(17.86,10.88,9.33,9.3,8.98,8.92,8.83,8.06,7.13,4.85,4.53,1.33)

w <- w/100
sum(w)

weights_tbl <- tibble(symbols,w)
weights_tbl
```
```{r}
weights_tbl %>%
  ggplot(aes(x = "", y = w, fill = symbols)) +
  geom_col() +
  coord_polar("y", start = 0) +
  theme(axis.text.x = element_blank()) + 
  geom_text(label = scales::percent(w), position = position_stack(vjust = 0.7)) +
  scale_fill_tq() + scale_color_tq() +
    labs(x = "", y = "", fill = "",
        title = "Asset weights in portfolio",
         caption = "Michael Burry's All Portfolio"
        )
```
# Creating Portfolio based on the weights scheme of Michael Burry
```{r}
portfolio_returns_tbl <- returns_monthly %>%
  group_by(symbol) %>%
  tq_portfolio(
    assets_col     = symbol,
    returns_col    = monthly.returns,
    weights        = weights_tbl,
    rebalance_on   = "months"
  ) %>%
  add_column(symbol = "Portfolio", .before = 1) %>%
  ungroup() %>%
  rename(monthly.returns = portfolio.returns) 

end_port_date <- last(portfolio_returns_tbl$date)
  

```
```{r}
g <- portfolio_returns_tbl %>%
    ggplot(aes(date, monthly.returns)) +
    geom_bar(stat = "identity",
             fill = palette_green()[[1]]) +
    theme_tq() +
  labs(
        x = "", y = "Portfolio Returns",
        title = "Portfolio Returns(2014-2022",
        
        caption = "Micahel Burry's  Portfolio"
    )

g
```
```{r}
ggplotly(g)
```
# Combining the portfolio_returns and stock returns together to visualize the returns over the period of time
# step1
```{r}
total_returns_tbl <- returns_monthly %>%
  bind_rows(portfolio_returns_tbl)

```
# step2 Visualization
```{r}
B <- total_returns_tbl %>%
  mutate(symbol = as.factor(symbol)) %>%
  
  ggplot(aes(date,monthly.returns)) +
  geom_smooth(data = portfolio_returns_tbl,aes(color = symbol), 
                se = FALSE, linetype = "dashed", color = "blue") +
  geom_smooth(data = returns_monthly, aes(color = symbol), se = FALSE,
                linetype = "solid") +
  scale_y_continuous(labels = scales::percent)  +
  theme_tq() +
  scale_color_tq() + 
  labs(title = "Monthly Returns of Portfolio vs Individual Stocks",
       subtitle = "Portfolio is in the dashed blue line",
       caption = "Michael Burry' Portfolio Performance") +
  
  annotate(geom = "text",
             x = end_port_date,
             y = -0.0015,
             label = "Portfolio",
             fontface = "plain",
             alpha = 2) 
B
  
  
 
```
```{r}
total_returns_tbl %>%
  group_by(symbol) %>%
  tq_performance(Ra = monthly.returns, 
                   performance_fun = SharpeRatio.annualized,
                   scale = 12,
                   Rf = 0.03/12) %>%
  ungroup() %>%
  mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`,2)) %>%
  ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() + 
    scale_color_tq() + 
    geom_label(nudge_y = -0.02) +
    labs(title = "Annualized Sharpe Ratio (RFR = 3%) ",
         subtitle = "AAPL has the max Sharpe Ratio and Discovery(WBD) exhibits  -ve Raito",
         caption = "Michael Burry's Portfolio",
         y = "Sharpe Ratio",
         x = "Ticker Symbol")

```

```{r}
returns_monthly %>%
  tq_portfolio(assets_col  = symbol,
               returns_col = monthly.returns,
               weights     = weights_tbl,
               rebalance_on = "years",
               wealth.index = TRUE) %>%
  mutate(investment_growth = portfolio.wealthindex * 10000) %>%
  select(date, investment_growth) %>%
  ggplot(aes(date, investment_growth)) +
  geom_line(stat = "identity") +
  geom_smooth(method = "loess") +
  theme_tq(base_size = 15) + scale_color_tq() +
  scale_y_continuous(labels = scales::dollar) +
  labs(
    title    = "Investment-Growth of Michael Burry's Portfolio",
    subtitle = "Intial Investment of $10000"
  )
```


