---
title: "Portfolio_Analysis_Tidy_Models"
author: "Mandar"
date: '2022-05-26'
output: 
 html_document:
    code_folding: show #or show
    df_print: paged #or tibble
    highlight: tango 
    number_sections: yes #or no
    theme: flatly #from bootswitch themes
    toc: yes #shows table of contents
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE)


```
# libraries


```{r}
library(tidyquant)
library(tidyverse)
library(lubridate)
library(purrr)
library(tidymodels)
library(timetk)
library(highcharter)
library(ggplot2)
library(tidyr)
library(webshot)

```
# Downloading the data 

```{r}
symbols <- c("VTI", "TLT", "IEF", "GLD", "DBC")
end <- Sys.Date() %>% ymd()
start <- end - years(17) + days(1)
raw_data <- symbols %>% 
    tq_get(get = "stock.prices",
           from = start,
           to = end)
```

# Checking for homogenity of the data
```{r}
raw_data %>%
    group_by(symbol) %>%
    summarise(
        min_date = min(date),
        max_date = max(date)
    )
# this shows the data is consistent for the date
```
```{r}
returns_tbl <- raw_data %>%
    select(symbol, date, adjusted) %>%
    group_by(symbol) %>%
    tq_transmute(
        select     = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly",
        type       = "log"
    ) %>%
    ungroup() %>%
    mutate(date = lubridate::rollback(dates = date, roll_to_first = TRUE))

returns_tbl
    



```
# Spreading the data. We could use spread() but here we use pivot_wider. Same functionality

```{r}

returns_tbl %>%
    group_by(symbol) %>%
    pivot_wider(names_from = symbol, values_from = monthly.returns) %>%
    ungroup() 
    
``` 
# ggplot fot visualization 
```{r}

g <- returns_tbl %>%
    ggplot(aes(monthly.returns)) +
    geom_density(aes(color = symbol), alpha = 0.3) +
    geom_histogram(aes(fill = symbol), alpha = 0.5, binwidth = 0.005) +
    guides(color = "none") +
    labs(
        title = "Monthly Spread of ETF Returns"
    ) +
    theme_tq() + theme(legend.position = "none") +
    facet_wrap(~ symbol, ncol = 3) +
    ylab("") +
    xlab("Monthly Returns") +
    scale_x_continuous(labels = scales::percent)
    
    
g

```
```{r}
library(plotly)
ggplotly(g)
```
# Visualization fo the Returns
```{r}
returns_tbl  %>%
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() +
    facet_wrap(~ symbol, scales = "free_y") +
    theme_tq() +
    scale_y_continuous(labels = scales::percent) + theme(legend.position = "none") +
    geom_smooth(method = "lm") +
    labs(
        title = "Monthly Returns of the Funds (2006-2022)",
        subtitle = " 2008 and to some extent 2020-21 have been the years of fluctuations",
        caption  = "All Season Fund",
        y = "Monthly Returns", x = ""
    )
```
# Visualization of the ETFs

```{r}
raw_data %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() +
    facet_wrap(~ symbol, scales = "free_y") +
    scale_y_continuous(labels = scales::dollar) +
    theme_tq() + scale_color_tq() +
    theme(legend.position = "none") +
    labs(
        title = "Adjusted Prices of the ETFs (2006-2022) ",
        subtitle = "Till 2020 all other than Gold & Commodity ETFs experience a rising trend",
        caption = " All Seasons Fund",
        y = "Adjusted Price", x = ""
    )
```
# Calculation of Sharpe Ratio for the returns
```{r}
S <- returns_tbl  %>%
    group_by(symbol) %>%
    tq_performance(
        Ra = monthly.returns,
        performance_fun = SharpeRatio.annualized,
        scale = 12,
        Rf = 0.03/12
    ) %>%
    ungroup() %>%
    mutate(symbol = as.factor(symbol)) %>%
    mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`,2)) %>%
    ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() + 
    scale_color_tq() + 
    geom_label(nudge_y = -0.05) +
    labs(title = "Annualized Sharpe Ratio (RFR = 3%)",
         subtitle = "Commodities fund (DBC) has negative sharpe ratio",
         caption = "Ray Dalio's All Weather Funds",
         y = "Sharpe Ratio",
         x = "Ticker Symbol")
S

    
```
```{r}
ggplotly(S)
```
# Creating the Portfolio based on the Ray Dalio's Philosophy


# first weights allocation 

```{r}
w <-  c(0.3,0.4,0.15,0.075,0.075)

wts_tbl <- tibble(symbols,w)

wts_tbl
```
# Visualization of the weight allocation

```{r}
wts_tbl %>%
    ggplot(aes(x = "", y = w, fill = symbols)) +
    # geom_bar(width = 1, stat = "identity") +
    geom_col() +
    coord_polar("y", start = 0) +
    theme(axis.text.x = element_blank())  + 
    geom_text(label = scales::percent(w), position = position_stack(vjust = 0.5)) +
    scale_fill_tq() +
    labs(x = "", y = "", fill = "",
        title = "Asset weights in portfolio",
         caption = "Ray Dalio's All Weather Funds"
        )
```
```{r}
returns_reg_tbl <- returns_tbl %>%
    group_by(symbol) %>%
    filter(date >= "2006-03-01")
returns_reg_tbl 
```

# Now we create the portfolio based on the weights
```{r}
portfolio_returns_tbl <- returns_reg_tbl %>%
    tq_portfolio(
        assets_col  =  symbol,
        returns_col =  monthly.returns,
        weights     =  wts_tbl,
       rebalance_on = "years"
    ) %>%
    add_column(symbol = "Portfolio", .before = 1) %>%
    rename(monthly.returns = portfolio.returns)
end_port_date <-  last(returns_tbl$date)
portfolio_returns_tbl
    
```
# Visualozation of Portfolio Returns

```{r}
T <- portfolio_returns_tbl %>%
    ggplot(aes(date, monthly.returns)) +
    geom_bar(stat = "identity",
             fill = palette_green()[[1]]) +
    theme_tq() +
    labs(
        x = "", y = "Portfolio Returns",
        title = "Portfolio Returns over the Period of time",
        subtitle = " 40 % TLT, 30% VTI, 15% IEF, 7.5% GLD, 7.5% DBC",
        caption = "Ray Dalio's All Season Portfolio"
    )
T
```

```{r}
combined_returns_tbl <- returns_reg_tbl %>%
    bind_rows(portfolio_returns_tbl)

```
# Comparing individual ETF returns with the portfolio returns
```{r}
 # Combining the returns
combined_returns_tbl <- returns_tbl %>%
    bind_rows(portfolio_returns_tbl)

```
# Comparison of Returns
```{r}
combined_returns_tbl %>%
    ggplot(aes(date, monthly.returns)) +
    geom_smooth(data = portfolio_returns_tbl,aes(color = symbol), 
                se = FALSE, linetype = "dashed", color = "blue") +
    geom_smooth(data = returns_tbl, aes(color = symbol), se = FALSE,
                linetype = "solid") +
    scale_y_continuous(labels = scales::percent) +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Monthly Returns of Portfolio vs Individual Fund",
         subtitle = "Portfolio is the dashed blue line",
         y = "Monthly Returns") + 
    annotate(geom = "text",
             x = end_port_date,
             y = 0.0015,
             label = "Portfolio",
             fontface = "plain") +
    annotate(geom = "text",
             x = end_port_date,
             y = 0.005,
             label = "GLD",
             fontface = "plain") +
    annotate(geom = "text",
     x = end_port_date,
     y = 0.008,
     label = "VTI",
     fontface = "plain") +
    annotate(geom = "text",
             x = end_port_date,
             y = -0.009,
             label = "IEF",
             fontface = "plain") +
    annotate(geom = "text",
             x = end_port_date,
             y = -0.015,
             label = "TLT",
             fontface = "plain") +
    annotate(geom = "text",
             x = end_port_date,
             y = 0.045,
             label = "DBC",
             fontface = "plain")



```

# Sharpe Ratio for Individual ETF and Portfolio
```{r}
combined_returns_tbl %>%
    group_by(symbol) %>%
    tq_performance(Ra = monthly.returns, 
                   performance_fun = SharpeRatio.annualized,
                   scale = 12,
                   Rf = 0.03/12) %>%
    ungroup() %>%
    mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`,2)) %>%
    ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() + 
    scale_color_tq() + 
    geom_label(nudge_y = -0.05) +
    labs(title = "Annualized Sharpe Ratio (RFR = 3%)",
         subtitle = "Commodities fund (DBC) has negative sharpe ratio",
         caption = "Ray Dalio's All Weather Funds",
         y = "Sharpe Ratio",
         x = "Ticker Symbol")
```
# Portfolio Growth
```{r}
portfolio_investment_tbl <- returns_reg_tbl %>%
    tq_portfolio(
        assets_col  =  symbol,
        returns_col =  monthly.returns,
        weights     =  wts_tbl,
       rebalance_on = "years",
       wealth.index = TRUE
    ) %>%
    mutate(investment_growth = portfolio.wealthindex * 100)

 portfolio_investment_tbl %>%
    ggplot(aes(date, investment_growth)) +
    geom_line(stat = "identity") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar) +
    labs(title = "All Seasons Fund Portfolio Growth",
         subtitle = "40% TLT, 30% VTI, 15% IEF, 7.5% GLD and 7.5% DBC",
         caption = "Ray Dalio's All Weather Funds",
         x = "",
         y = "Investment Growth")

I


    
```
# Putting it altogether
```{r}
wt <- c(0.3, 0.4, 0.15, 0.075, 0.075,
         1, 0, 0, 0, 0,
         0, 1, 0, 0, 0,
         0, 0, 1, 0, 0,
         0, 0, 0, 1, 0,
         0, 0, 0, 0, 1)

weights_tbl <- tibble(symbols) %>% 
    tq_repeat_df(n = 6) %>% 
    bind_cols(tibble(wt)) %>% 
    group_by(portfolio) 

weights_tbl  %>%
    ungroup() %>%
    mutate(wt = paste0(wt*100,"%")) %>%
    pivot_wider(names_from = symbols,
                values_from = wt) %>%
    mutate(portfolio = case_when(
        portfolio ==1 ~ "All Weather Portfolio",
        portfolio ==2 ~ "VTI",
        portfolio ==3 ~ "TLT",
        portfolio ==4 ~ "IEF",
        portfolio ==5 ~ "GLD",
        portfolio ==6 ~ "DBC"
    ))

```
# Visualize the growth in investment of $10000
```{r}
returns_multi_reg_tbl <- returns_reg_tbl %>% 
    ungroup() %>% 
    tq_repeat_df(n = 6)
returns_multi_reg_tbl
port_returns_invest_tbl <- returns_multi_reg_tbl %>%
    tq_portfolio(assets_col = symbol,
                 returns_col = monthly.returns,
                 weights = weights_tbl,
                 wealth.index = TRUE) %>%
    mutate(investment_growth = portfolio.wealthindex * 10000)

end_port_date <- last(port_returns_invest_tbl$date)

    
```
```{r}
K <- port_returns_invest_tbl %>%
    ungroup() %>% 
    mutate(portfolio = case_when(portfolio == 1 ~ "All Seasons Portfolio",
                                 portfolio == 2 ~ "VTI",
                                 portfolio == 3 ~ "TLT",
                                 portfolio == 4 ~ "IEF",
                                 portfolio == 5 ~ "GLD",
                                 portfolio == 6 ~ "DBC")) %>% 
    mutate(portfolio = as.factor(portfolio)) %>% 
    ggplot(aes(x = date, y = investment_growth, colour = portfolio)) + 
    geom_line(stat = "identity") + 
    geom_smooth(method = "loess") +
    theme_tq() + 
    scale_color_tq() + 
    scale_y_continuous(labels = scales::dollar) + 
    labs(title = "All Seasons Fund Portfolio Growth vs Standalone Security Growth",
         subtitle = "40% TLT, 30% VTI, 15% IEF, 7.5% GLD and 7.5% DBC",
         caption = "Ray Dalio's All Weather Funds",
         x = "",
         y = "Investment Growth") +
    annotate(geom = "text",
             x = end_port_date,
             y = 24000,
             label = "Portfolio",
             fontface = "plain")

K
```
```{r}
library(plotly)

ggplotly(K)
```
```{r}
high_chart_xts <- port_returns_invest_tbl %>%
    ungroup() %>% 
    mutate(portfolio = case_when(portfolio == 1 ~ "All Seasons Portfolio",
                                 portfolio == 2 ~ "VTI",
                                 portfolio == 3 ~ "TLT",
                                 portfolio == 4 ~ "IEF",
                                 portfolio == 5 ~ "GLD",
                                 portfolio == 6 ~ "DBC")) %>% 
    select(-portfolio.wealthindex) %>% 
    pivot_wider(names_from = portfolio, values_from = investment_growth) %>% 
    tk_xts(date_var = date,
           silent = TRUE)


```
```{r}
highchart(type = "stock") %>% 
    hc_title(text = "All Seasons Fund Portfolio Growth vs Standalone Security Growth") %>% 
    hc_add_series(high_chart_xts[, 1], 
                  name = "Portfolio") %>% 
    hc_add_series(high_chart_xts[, 2],
                  name = symbols[1]) %>% 
    hc_add_series(high_chart_xts[,3],
                  name = symbols[2]) %>% 
    hc_add_series(high_chart_xts[,4],
                  name = symbols[3]) %>% 
    hc_add_series(high_chart_xts[,5],
                  name = symbols[4]) %>% 
    hc_add_series(high_chart_xts[,6],
                  name = symbols[5]) %>%
    # hc_tooltip(pointFormat = '{series.name}
    #            ${point.y:,.0f}')
    hc_tooltip(pointFormat =
    "<span style=\"color:{series.color}\">{series.name}</span>:<b>${point.y:,.0f}</b><br/>",
        shared=TRUE)

```











