---
title: "Real-Estate-Sector"
format: html
code-fold: true

editor: visual
---

```{r}
knitr::opts_chunk$set(echo = TRUE,fig.align = "center",
                        message = FALSE,
                      warning = FALSE)
options(tinytex.verbose = TRUE)
```

# Loading the Libraries

```{r}
library(tidymodels)
library(tidyquant)
library(tidyverse)
library(scales)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(plotly)
library(timetk)
library(modeltime)
library(DataExplorer)
library(correlationfunnel)

```

# The real estate sector generally includes two different types of investments related to real estate. Some stocks in the sector are responsible for developing new real estate projects and then managing them by obtaining tenants for various spaces within the project property. In addition, most real estate investment trusts, which are special tax-favored business entities that operate in various areas of the real estate industry, get counted as within the real estate sector.

```{r}
# tickers
symbols <- c("WELL","WY","LPX","DRE","PEAK") %>% sort()
# prices
# stock prices
prices  <- symbols %>%
    tq_get(get = "stock.prices", from = "1990-01-01")
# returns
returns <- prices %>%
    group_by(symbol) %>%
    tq_transmute(
        select = adjusted,
        mutate_fun = periodReturn,
        period     = "monthly",
    ) %>%
    ungroup() %>%
    mutate(date = rollback(date, roll_to_first = TRUE))
returns


```

# Visualization of the Returns

```{r}
returns %>%
    group_by(symbol) %>%
    ggplot(aes(date, monthly.returns, color = symbol)) +
    geom_line() + scale_y_continuous(labels = scales::percent) +
    theme_tq() + facet_wrap(~symbol) + 
    labs(
        title = "Monthly returns",
        subtitle = "Real Estate Sector",
        x = "",
        y = "Monthly Returns"
    ) + theme(legend.position = "none")

```

# Stock Prices Visualization

```{r}
prices %>%
    group_by(symbol) %>%
    plot_time_series(
        .date_var = date,
        .value = adjusted,
        .color_var = symbol,
        .facet_ncol = 2,
        .facet_scales = "free_y",
        .smooth = FALSE,
        .title = "Stock Prices Real Estate Sector",
        .x_lab = "",
        .y_lab = "Adjusted Prices",
        .legend_show = FALSE
    )

```

# Portfolio Construction

```{r}
# Weights Allocation
w <- rep(1/5, 5)
# Portfolio creation
port_ret_tbl <- returns %>%
    tq_portfolio(
        assets_col = symbol, 
        returns_col = monthly.returns,
        weights = w
    ) %>%
    mutate(date = rollback(date, roll_to_first = TRUE)) %>%
    add_column(symbol ="Portfolio", .before = 1)

#Visualization
port_ret_tbl  %>%
    ggplot(aes(date, portfolio.returns)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous(labels = scales::percent) + theme_tq() + scale_color_tq() +
    labs(
        title = "Portfolio Returns",
        subtitle = "Real Estate Sector",
        y = "Returns",
        x = ""
    )
```

# timetk

```{r}
port_ret_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = portfolio.returns,
        .title = "Portfolio Returns Real Estate Sector",
        .x_lab = "",
        .y_lab = "Returns"
    )
```

# S&P500

```{r}
market_prices <- tq_get("^GSPC", get = "stock.prices",from = "1990-01-01")
market_returns <-  market_prices %>%
    tq_transmute(select = adjusted,
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "market_ret") %>%
    mutate(date = rollback(date, roll_to_first = TRUE))
market_returns
```

#  FAMA-FRENCH FACTORS

```{r}
library(frenchdata)
factors_ff_monthly_raw <- download_french_data("Fama/French 3 Factors")
factors_ff_monthly <- factors_ff_monthly_raw$subsets$data[[1]] |>
  transmute(
    date = floor_date(ymd(str_c(date,"01")),"month"),
    rf = as.numeric(RF) / 100,
    mkt_excess = as.numeric(`Mkt-RF`) / 100,
    smb = as.numeric(SMB) / 100,
    hml = as.numeric(HML) / 100
  ) %>%
  # filter the dates 
  filter(date >= "1990-01-01")

factors_ff_monthly 
```

# Combining all the data

```{r}
port_risk_market_tbl <- port_ret_tbl %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = portfolio.returns - rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    select(symbol, date, mkt_excess, smb, hml, excess_returns, market_excess_returns)
port_risk_market_tbl
```

# \# Beta Estimation 

## step1:CAPM function

```{r}
library(slider)
# estimate capm
estimate_capm <- function(data, min_obs = 1) {
  if (nrow(data) < min_obs) {
    beta <- as.numeric(NA)
  } else {
    fit <- lm(excess_returns ~ mkt_excess + smb+hml+ market_excess_returns, data = data)
    beta <- as.numeric(fit$coefficients[2])
  }
  return(beta)
}
# rolling capm estimation
roll_capm_estimation <- function(data, months, min_obs) {
  data <- bind_rows(data) |>
    arrange(date)

  betas <- slide_period_vec(
    .x = data,
    .i = data$date,
    .period = "month",
    .f = ~estimate_capm(., min_obs),
    .before = months - 1,
    .complete = FALSE
  )

  tibble(
    month = unique(data$date),
    beta = betas
  )
}
```

## step2: Estimation

```{r}
beta_port_tbl <- port_risk_market_tbl %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    drop_na() %>%
    select(symbol, date, beta)

beta_port_tbl
```

## step3: Beta Visualization

```{r}
beta_port_tbl %>%
    ggplot(aes(date, beta)) +
    geom_line() + geom_smooth(method = "loess") +
    scale_y_continuous() + theme_tq() + scale_color_tq() +
    labs(
        title = "Rolling Beta using 5 years data",
        subtitle = "Real Estate Sector",
        caption = "Stocks(DRE, LPX, PEAK, WELL, WY)",
        x ="",
        y="Beta"
    )
```

# Stocks Returns, Fama-French and Market Index

```{r}
# combining the data
returns_risk_market_tbl <- returns %>%
    group_by(symbol) %>%
    left_join(factors_ff_monthly, by = "date") %>%
    left_join(market_returns, by = "date") %>%
    mutate(excess_returns = monthly.returns -rf) %>%
    mutate(market_excess_returns = market_ret - rf) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, excess_returns, market_excess_returns, mkt_excess, smb, hml)
returns_risk_market_tbl
```

# Beta Estimation for Stocks

```{r}
beta_stocks_tbl <- returns_risk_market_tbl %>%
    group_by(symbol) %>%
    mutate(roll_capm_estimation(cur_data(), months = 60, min_obs = 48)) %>%
    ungroup() %>%
    drop_na() %>%
    select(symbol, date, beta)
beta_stocks_tbl
```

# Beta Visualization

```{r}

beta_stocks_tbl %>%
    ggplot(aes(date, beta, color = symbol)) +
    geom_line() + scale_y_continuous() +
    theme_tq() +
    labs(
        title = "Rolling beta with 5 years of data",
        subtitle = "Real Estate Sector ",
        capition = "stocks(DRE, WELL,WY, LPX, PEAK)",
        y ="Beta",
        x =""
    ) 
```

# timetk

```{r}
beta_stocks_tbl %>%
    plot_time_series(
        .date_var = date,
        .value = beta,
        .color_var = symbol,
        .smooth = FALSE,
        .title = "Rolling Beta for Stocks (Real Estate Sector)",
        .x_lab = "",
        .y_lab = "Beta"
    )
```
